### 2017-10-20 paper/sexSelectionSpacing-ver1.tex
Add stand-alone bib file
Update median duration tables with loop over education

[Only a subset of the planned analyses to demonstrate the method and interpretation]

@@

\onehalfspacing
\bibliographystyle{aer}
\bibliography{collection}

>>>>

% Median duration and sex ratio tables
\input{../tables/median_sex_ratio_low.tex}

\input{../tables/median_sex_ratio_med.tex}

\input{../tables/median_sex_ratio_high.tex}

\subsection{[Specific spell/education/area combinations of special interest]}
[Only a subset of the planned analyses to demonstrate the method and interpretation]

@@

\onehalfspacing
\bibliographystyle{aer}
\bibliography{sex_selection_spacing}
